Multi-view 3D Aerosol Distribution Recovery

### 2013-07-27 article.tex
bookmark

Consider a set of ground-based wide-angle cameras
% ~\cite{Cossairt2011, Peleg01omnistereo:panoramic,
% Koppal:2011:WMS:2191740.2192152}
looking upwards (\cref{fig:groundgrid}). The set performs {\em
  integral imaging}~\cite{integral} of the sky. Per viewpoint, the
view azimuth and elevation angles (relative to the zenith and north)
are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location ${\bm x}$, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
a principle of estimating the 3D atmospheric aerosols distribution,
using such data. To show feasibility, we perform radiative transfer
using two different forward models, enabling cross-validation.  A
forward model takes as input the 3D aerosol distribution, and outputs
images as if captured at various viewpoints. One model uses Monte
Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic,
slow but naturally expresses multiple-scattering. Hence, this approach
simulates realistic scenes of arbitrary complexity.  The second model
uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves radiative transfer in an analytic, closed form. This form enables simple inversion of the model, to
estimate the underlying atmosphere (\cref{sec:inverse-problem}).

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).
    [c] Cross section along the
  }
  \label{fig:simulation-results1}
\end{figure}

@@

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:extinctc}, the total optical depths
corresponding to LOSs (of camera $c$) and SRs that cross all voxels
comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;.
  \label{eq:tautotal}
\end{equation}

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$.
%Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
coefficients across the domain are expressed in vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
      \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,
      \quad
%  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
%  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
%    g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \tilde{\vect{\alpha}}^{\rm aerosol}_c =
       \varpi^{\rm aerosol} \sigma^{\rm aerosol}
        {\bm n} \odot P^{\rm aerosol}_{\bm g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
%The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
%the phase function, in all voxels. This notation indicates a
%parametric phase function as in \cref{eq:aerosol_scatter}.
Here the operator $\odot$ denotes the Hadamard (element-wise)
product.

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being oblivious to all the rest~(\cref{fig:projection}b).
% \begin{figure}
%   \centering
%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
%   voxels above it on a SR. The scattered radiance from voxel $k$ is
%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
%   image pixel captures light emanating in a cone in space. Voxels
%   that fully or partially fall in this cone are sensed by the
%   pixel.}
%   \label{fig:projection}
% \end{figure}
Overall, light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a
vector $N_{\rm pix}$ long.
Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
%\begin{align}
%  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
%    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
%      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
%    (\vect{\sigma} \odot {\bm n})]\} \right\}
%  \label{eq:bigIc}
%\end{align}
%We focus on situations where there is only a single
%type of aerosol over a scene. Hence, the three-element vector
%$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
%the scene, but the density distribution ${\bm n}$ is variable. Then,
%\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
    scatter}_c) \odot{\bm n} ]
  \odot
  \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c{\bm n})]
    \Big\} .
  \label{eq:bigIA}
\end{align}

@@

Monte Carlo (MC) methods enable rigorous modeling of photon
propagation in the atmosphere. The radiative transfer is expressed as
probability distributions which describe the distance travelled by the
photon in-between scatterings and the angle of deflection at each
scatter.  This enables simulating multiple scattering and produce
realistic results.  MC simulations can be made arbitrarily accurate by
increasing the number of photons.  Another advantage of the MC methods
is that they are highly parallelizable.

The MC simulations use the same atmosphere grid described in
\cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
traced from the detector, camera, to their source, sun. Photons are
emitted from each pixel of the camera in the direction determined by
the camera model, i.e. hemispherical camera. The quality of the
simulations is proportional to the number of photons. To create the
\cref{fig:simulation-results1}b \num{10000} photons were emitted from
each pixel. The distance travelled by the photon till its first
scattering is determined by inversion sampling the transmittance
probability (\cref{sec:theor-backgr}) optical distance
distribution. This is done using the inversion sampling method. Once
the optical distance is determined the ``real'' distance is determined
by summing the optical depth of the discrete voxels
(\cref{sec:optical-depth}) along the photon direction till the desired
optical distance is reached.  At each scattering event, first the type
of aerosol is determined by sampling the different aerosols
distributions inside the voxel. The new direction is determined by
inverse sampling the phase function of the relevant aerosols:
Rayleigh, \cref{eq:rayleighP} or Henyey-Greenstein
\cref{eq:aerosol_scatter}.  To accelerate the MC we use the local
estimation (LE) method.

@@

In this paper, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.
%Most generally, this is the set
%$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
%        g}_{\lambda}\right\}_{\lambda}\right\}$
%where some of the parameters depend on the spectral channel $\lambda$.
%Usually, a single aerosol type dominates a scene. Furthermore, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.
At hand, we have $N_{\rm views}$ measured photographs
 $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased as
optimization of an objective function that fits the image-formation model to the measured photographs:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around
the sun, which are overwhelmingly bright. %and the horizon.
%These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term that expresses some prior knowledge on the distribution, while $\eta$ is a regularization weight.  Since aerosol distributions are usually fuzzy,
it can be beneficial that regularization be a {\em smoothness term}, which penalized energy in second order spatial derivatives (3D Laplacian). Hende, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D \emph{Laplacian}
operator.

@@

>>>>

Consider a set of ground-based wide-angle cameras
% ~\cite{Cossairt2011, Peleg01omnistereo:panoramic,
% Koppal:2011:WMS:2191740.2192152}
looking upwards (\cref{fig:groundgrid}). The set performs {\em
  integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
view azimuth and elevation angles (relative to the zenith and north)
are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location ${\bm x}$, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
a principle of estimating the 3D atmospheric aerosols distribution,
using such data. To show feasibility, we perform radiative transfer
using two different forward models, enabling cross-validation.  A
forward model takes as input the 3D aerosol distribution, and outputs
images as if captured at various viewpoints. One model uses Monte
Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic,
slow but naturally expresses multiple-scattering. Hence, this approach
simulates realistic scenes of arbitrary complexity.  The second model
uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves radiative transfer in an analytic, closed form. This form
enables simple inversion of the model, to estimate the underlying
atmosphere (\cref{sec:inverse-problem}).

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:tau}, the total optical depths
corresponding to LOSs (of camera $c$) and SRs that cross all voxels
comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;.
  \label{eq:tautotal}
\end{equation}

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$.
% Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in
% all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
coefficients across the domain are expressed in vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,
  \quad
  % \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
  % \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
  % g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \tilde{\vect{\alpha}}^{\rm aerosol}_c =
  \varpi^{\rm aerosol} \sigma^{\rm aerosol}
  {\bm n} \odot P^{\rm aerosol}_{\bm g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
% The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter
% of the phase function, in all voxels. This notation indicates a
% parametric phase function as in \cref{eq:aerosol_scatter}.
Here the operator $\odot$ denotes the Hadamard (element-wise) product.

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being
oblivious to all the rest.
Overall, light power captured at a pixel is a weighted sum of the
power $p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
  pix}$ long.  Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured
image is thus
% \begin{align}
%   {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
%     (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
%     aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
%     (\vect{\sigma} \odot {\bm n})]\} \right\}
%   \label{eq:bigIc}
% \end{align}
% We focus on situations where there is only a single type of aerosol
% over a scene. Hence, the three-element vector $[{\sigma}^{\rm
% aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
% the density distribution ${\bm n}$ is variable. Then,
% \cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
  {\bm D}_c{\bm n})] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

Monte Carlo (MC) methods enable rigorous modeling of photon
propagation in the atmosphere.  MC simulations can be made arbitrarily
accurate by increasing the number of launched photons. MC methods are
highly parallelizable. When applied to the RT problem, they enable
simulating multiple scattering and produce realistic results.

The MC simulations use the same atmospheric grid described in
\cref{sec:single-scatt-model}. We use backward MC, i.e. photons are
traced from the detector, camera, to their source, the Sun, in a
direction determined by the camera model, i.e. hemispherical
camera. The quality of the simulations is proportional to the number
of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
photons were emitted from each pixel. The distance travelled by the
photon till its first scattering is determined by sampling from the
transmittance distribution using the inverse transform sampling
(\cref{sec:theor-backgr}).  The CDF of the transmittance distribution
is given by,
\begin{equation}
  \label{eq:1}
  F=\int_{0}^{1}\exp(-\tau)\derivsym{\tau}=1-\exp(-\tau)
\end{equation}
Given a uniformly distributed random number $u$ a random transmittance
is given by
\begin{equation}
  \label{eq:2}
  t=F^{-1}(u)=-\ln(1-u)
\end{equation}
If the scattering occurs outside the atmospheric grid, the photon is
dropped. If not, the voxel in which the scattering occurs is
calculated.  The type of scattering, either by air molecule or aerosol
particle, is determined randomly according to their relative densities
in the voxel.  The new direction of the photon is determined by
inverse sampling the phase function of the scattering particle:
Rayleigh, \cref{eq:rayleighP}, or Henyey-Greenstein,
\cref{eq:aerosol_scatter}.  Local Estimation~\cite{marshak20053d} is
used for calculating the amount of light reaching the sun at each
scattering.  This process is repeated till the photon escapes the
atmosphere grid or it reaches a predetermined number of scatterings.

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the }
  \label{fig:simulation-results1}
\end{figure}
To test the model, we simulated several atmospheric models. Here are
the details.

\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
  50}{\km} extending from the ground up to altitude of
\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
different grid sizes from \num{50 x 50 x 100} grid, where each voxel
has area of \SI{1 x 1}{\km} and vertical thickness of \SI{100}{\metre}
and down to \num{10 x 10 x 20} grid, where each voxel has area of
\SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}.

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in Ref.~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$.

We simulated various spatial distributions, as a product of two
functions. The first function is an exponential decay~\cite{Levi1980}
with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \frac{1} {n^{sea level}}
  \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height.

\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
field of view, capturing the entire sky from its viewpoint. We used
different numbers of cameras ranging from 12 viewpoints to 100, on a
grid.  The resolution of each camera is low, expressing the fact that
cloudless (yet hazy) sky images are rather smooth.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution ${\bm n}$.
% Most generally, this is the set $\left\{{\bm
%   n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
%     g}_{\lambda}\right\}_{\lambda}\right\}$ where some of the
% parameters depend on the spectral channel $\lambda$.  Usually, a
% single aerosol type dominates a scene. Furthermore, we assume that
% the type of the aerosol above an area is
% known~\cite{Martonchik2009}. Hence, we focus on estimating the
% density distribution ${\bm n}$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around the sun, which are
overwhelmingly bright. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.  Since aerosol distributions are usually
fuzzy, it can be beneficial that regularization be a {\em smoothness
  term}, which penalized energy in second order spatial derivatives
(3D Laplacian). Hende, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D
\emph{Laplacian} operator.

@@

We applied the reconstruction algorithm \cref{sec:inverse-problem} to
the images simulated in \cref{sec:simul}. We used the L-BFGS-B
algorithm~\cite{BFGS} on a computer cluster. Each core was dedicated
to rendering a modeled image. The algorithm was initialized by ${\bm
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total.
